### 2016-03-23 section/0_intro.tex
submitted version

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC27733.c}}
\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch)}
\label{fig:GCC27733}
\end{figure}

@@

\begin{itemize}
\item Focused checking. 
Different from performance-bug detectors that blindly checks the whole
software, \Tool focuses on loops that are
most correlated with performance symptoms. 
This focus is crucial for \Tool to achieve both high
accuracy and high coverage.

>>>>

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC27733.c}}
\caption{A real-world performance bug in GCC (the `-' and `+' demonstrate the patch; variable and 
function names are simplified for demonstration purposes)}
\label{fig:GCC27733}
\end{figure}

@@

\begin{itemize}
\item Focused checking. 
Different from performance-bug detectors that blindly check the whole
software, \Tool focuses on loops that are
most correlated with performance symptoms. 
This focus is crucial for \Tool to achieve both high
accuracy and high coverage.

### 2016-03-23 section/1_under.tex
submitted version

Previous work has identified a wide variety of performance root-cause 
categories. However, no existing taxonomy satisfies all the three 
requirements below and hence cannot be directly used for our diagnosis tool
design.
\begin{enumerate}
\item Coverage: covering
a big portion of real-world inefficient loop problems; 
\item Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
\item Generality: application-specific root causes will not work, as we
hope to build diagnosis tools that can automatically identify root causes 
without developers' help.
\end{enumerate}

@@

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\label{fig:GCC46401}
\end{figure}

{\textbf{[0$|$1]*}}:
Each iteration in this type of loops may or may not produce results.
For some workload, the majority of iterations do not produce
results and cause performance problems perceived by users.
These problems are often solved
by adding a simple check to conditionally skip the expensive loop.
Figure~\ref{fig:GCC46401} shows such an example.
%how users perceive this problem
%explain how every iteration may or may not produce any results
%explain the fix
Users complained that compilation became extremely slow when
the \texttt{-Wsequence-point} checking is enabled.
The slowness was caused
by the \texttt{for} loop in the figure. As the algorithm
behind this loop has quadratic complexity in the number of operands in an expression, 
programs with long expressions suffer severe slow-downs.
After further diagnosis, developers observed that this loop rarely
had any side-effects, as the \texttt{if} condition was rarely satisfied.
At the end, the patch greatly improved performance through a
simple checking that allows the loop to be
skipped in most cases.

@@

{\textit{How to fix?}}
As we can see, a deep understanding of software semantics is required
to understand the inefficiency root cause of these loops.
Similarly, the fix strategies for these loops would vary from case to case.
%At high level, the patch often involves skip some computation that produces
%side effects that are useless due to semantic reasons.

@@

{\textit{How to fix?}}
Intuitively, most redundancy problems can be fixed through memoization or
batching --- either caching the earlier computation results and skip
some of the following iterations; or combining multiple iterations' work
together.

For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
redundant computation across different invocations of recursive function
\texttt{mult\_alg}. The patch essentially allows memoization to work.
%Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
%This bug is fixed by using a hash table to avoid visiting the same sub-tree twice.
\comment{
Mozilla\#490742 in Figure~\ref{fig:Mozilla490742} represents a slightly different type of cross-iteration
redundancy. The inefficient loop in this case saves one URL into the ``Favorite
Links'' database in each iteration. One database transaction in each iteration
turns out to be to time consuming, with too much redundant work across
iterations. At the end, developers decide to batch all database updates into 
one big transaction, which speeds up some workload like 
bookmarking 50 tabs 
from popping up timeout windows to not blocking.
%xxx from several minutes
%to a couple of seconds.
}

@@

{\textit{How to fix?}}
Just like that in cross-iteration redundancy, memoization and batching
are the typical fix strategies for this type of redundancy problems ---
caching the earlier computation results and skip following redundant loops;
or combining multiple loop instances together to avoid or alleviate redundancy.

Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
The buggy loop counts how many previous siblings of the input \texttt{aNode} have the same name and URI. 
There is an outer loop, not shown in the figure, that repeatedly updates
\texttt{aNode} to be its next sibling and calls
\texttt{sss\_xph\_generate} with the new \texttt{aNode}. 
This bug is fixed by adding an extra field for each node to save the calculated 
count, so that a new count value can be calculated by simply adding one to the
saved count value of the nearest previous sibling with the same name and URI.

@@

\subsection{Discussion}
Coverage, actionability, and generality are the principles behind our taxonomy
design. Intuitively, the categories above cover a lot of common inefficient
loop problems; each sub-category is concrete enough to guide the design of a
failure diagnosis tool; none of the categories above involve any application
specific knowledges or heuristics. We will further assess our taxonomy
through the design of \Tool (Section \ref{sec:design}) and 
real-world bug study (Section \ref{sec:eval_taxonomy}).

>>>>

Previous work has identified a wide variety of performance root-cause 
categories. However, existing taxonomies do not satisfy all the three 
requirements below and hence cannot be directly used to guide our 
diagnosis-tool
design.
\begin{enumerate}
\item Coverage: covering
a big portion of real-world inefficient loop problems; 
\item Actionability: each root-cause category should be informative enough 
to help developers
decide how to fix a performance problem; 
\item Generality: application-specific root causes will not work, as we
hope to build diagnosis tools that can automatically identify root causes 
without developers' help.
\end{enumerate}

@@

{\textbf{[0$|$1]*}}:
Each iteration in this type of loops may or may not produce results.
For some workload, the majority of iterations do not produce
results and cause performance problems perceived by users.
%These problems are often solved
%by adding a simple check to conditionally skip the expensive loop.
Figure~\ref{fig:GCC46401} shows such an example.
%how users perceive this problem
%explain how every iteration may or may not produce any results
%explain the fix
Users complained that compilation became extremely slow when
the \texttt{-Wsequence-point} checking is enabled.
The slowness was caused
by the \texttt{for} loop in the figure. As the algorithm
behind this loop has quadratic complexity in the number of operands in an expression, 
programs with long expressions suffer severe slow-downs.
After further diagnosis, developers observed that this loop rarely
had any side-effects, as the \texttt{if} condition was rarely satisfied.
At the end, the patch greatly improved performance through a
simple checking that allows the loop to be
skipped in most cases.

\begin{figure}[t!]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\label{fig:GCC46401}
\end{figure}

@@

{\textit{How to fix?}}
Since a deep understanding of software semantics is required
to understand the inefficiency of these loops,
the fix strategies for these loops will likely vary from case to case.
%At high level, the patch often involves skip some computation that produces
%side effects that are useless due to semantic reasons.

@@

{\textit{How to fix?}}
Intuitively, most redundancy problems can be fixed through memoization or
batching --- either caching the earlier computation results and skip
some of the following iterations; or combining multiple iterations' work
together.
For example, the GCC bug shown in Figure~\ref{fig:GCC27733} is caused by
redundant computation across different invocations of recursive function
\texttt{mult\_alg}. The patch essentially enables memoization.
%Another bug similar to GCC\#27733 is shown in Figure~\ref{fig:GCC1687}. 
%This bug is fixed by using a hash table to avoid visiting the same sub-tree twice.
\comment{
Mozilla\#490742 in Figure~\ref{fig:Mozilla490742} represents a slightly different type of cross-iteration
redundancy. The inefficient loop in this case saves one URL into the ``Favorite
Links'' database in each iteration. One database transaction in each iteration
turns out to be to time consuming, with too much redundant work across
iterations. At the end, developers decide to batch all database updates into 
one big transaction, which speeds up some workload like 
bookmarking 50 tabs 
from popping up timeout windows to not blocking.
%xxx from several minutes
%to a couple of seconds.
}

@@

{\textit{How to fix?}}
Just like that in cross-iteration redundancy, memoization and batching
are the typical fix strategies for this type of redundancy problems ---
caching the earlier computation results and skip following redundant loops;
or combining multiple loop instances together to avoid or alleviate redundancy.
Mozilla\#477564 shown in Figure~\ref{fig:Mozilla477564} is an example for this type of bugs. 
The buggy loop counts how many previous siblings of the input \texttt{aNode} have the same name and URI. 
There is an outer loop, not shown in the figure, that repeatedly updates
\texttt{aNode} to be its next sibling and calls
\texttt{sss\_xph\_generate} with the new \texttt{aNode}. 
This bug is fixed by adding an extra field for each node to save the calculated 
count, so that a new count value can be calculated by simply adding one to the
saved count value of the nearest previous sibling with the same name and URI.

@@

\subsection{Discussion}
Coverage, actionability, and generality are the principles behind our taxonomy
design. Intuitively, the categories above cover a lot of common inefficient
loop problems; each sub-category is concrete enough to guide the design of a
failure diagnosis tool; none of the categories above involve any application
specific knowledges or heuristics. We will further assess our taxonomy
through the design of \Tool (Section \ref{sec:design}) and 
a real-world bug study (Section \ref{sec:eval_taxonomy}).

### 2016-03-23 section/2_workless.tex
split study section. the benchmark study does not guide study, but evaluate study
submitted version

\section{\Tool design}
\label{sec:design}
\Tool consists of a series of analysis that
judges whether a given loop belongs to any root-cause type discussed in
Section \ref{sec:study_tax}.
Its design
follows the following principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

@@

\subsubsection{Static Analysis}
\label{sec:s_workless}

@@

%TODO Shan will rewrite the next two paragraphs
\subsubsection{Dynamic Monitoring}
\label{sec:d_workless}

Except for 0*, none of the other three type of loops are inefficient for sure.
We need dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop worths fixing.

For a 0*1? loop, since it only generates results in the last iteration, we 
only need to know the total number of loop iterations 
to figure out the loop
\textit{resultful rate}, which we define as the ratio between
the number of iterations with
side effects and the total number of iterations. 
The implementation is straightforward
--- we initialize a local counter to be 0 in the pre-header of the loop; we 
increase the counter by 1 in the loop header to count the number of 
iterations; we dump that counter to log when the loop exits.

>>>>

\section{\Tool design}
\label{sec:design}
\Tool consists of a series of analysis that
judges whether a given loop belongs to any root-cause type discussed in
Section \ref{sec:study}.
Its design
follows three principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
or profilers,
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

@@

\subsubsection{Static analysis}
\label{sec:s_workless}

@@

%TODO Shan will rewrite the next two paragraphs
\subsubsection{Dynamic monitoring}
\label{sec:d_workless}

Except for 0*, none of the other three types of loops are inefficient for sure.
We need dynamic analysis to figure out what portion of loop iterations are
resultless at run time, which will help decide whether the loop worths fixing.

For a 0*1? loop, since it only generates results in the last iteration, we 
only need to know the total number of loop iterations of each loop instance
to figure out the loop
\textit{resultful rate}, which we define as the ratio between
the number of iterations with
side effects and the total number of iterations. 
The implementation is straightforward
--- we initialize a local counter to be 0 in the pre-header of the loop; we 
increase the counter by 1 in the loop header to count the number of 
iterations; we dump that counter to log when the loop exits.

### 2016-03-23 section/3_redundancy.tex
submitted version

\emph{How to suggest the most suitable fix strategy?}
As discussed in Section \ref{sec:study_ob} and Table \ref{tab:root},
memoization and batching are both common fix strategies for redundant loops.
To pick the right strategy,
extra analysis is conducted by \Tool and presented in 
Section \ref{sec:redundant_fix}.

@@

\subsubsection{Fix strategy recommendation}
\label{sec:redundant_fix}
\Tool suggests how to fix an inefficient loop to developers.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there is often only one or two natural fix 
strategies for each sub-category of root causes.

@@

For cross-iteration redundancy, \Tool suggests batching if the
redundancy is related to I/O operations and suggests memoization otherwise.
Specifically, 
when the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, \Tool reports 
this
as an I/O related redundancy problem and suggests batching as a potential fix
strategy. Otherwise, \Tool suggests memoization.

@@

In addition to the above high-level fix strategies, \Tool can also provide some 
detailed information to help developers design the patch.
For example, in case of memoization fix strategy,
since \Tool knows what exactly are the memory reads that return the same values
again and again, it can help decide what to memoize; in case of
I/O-related batching, \Tool points out the exact I/O operations that should
be considered batching; and so on. 
Generating the exact patch is out of the scope of \Tool.

>>>>

@@

\subsection{Fix Strategy Recommendation}
\label{sec:redundant_fix}
\Tool suggests how to fix an inefficient loop to developers.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there is often only one or two natural fix 
strategies for each sub-category of root causes.

@@

For cross-iteration redundancy, \Tool suggests batching if the
redundancy is related to I/O operations and suggests memoization otherwise.
Specifically, 
when the only side effect of a loop is from I/O operations
and the same statement(s) is executed in every loop iteration, \Tool reports 
this
as an I/O related redundancy problem and suggests batching as a potential fix
strategy. Otherwise, \Tool suggests memoization.

@@

In addition to the above high-level fix strategies, \Tool can also provide some 
detailed information to help developers design the patch.
For example, in case of memoization fix strategy,
since \Tool knows what exactly are the memory reads that return the same values
again and again, it can help decide what to memoize; in case of
I/O-related batching, \Tool points out the exact I/O operations that should
be considered batching; and so on. 
Generating complete patches is out of the scope of \Tool.

### 2016-03-23 section/5_exper.tex
submitted version

\paragraph{Benchmarks}
Note that \Tool is a tool that helps diagnose performance problems that
have already manifested, not a detection tool that can help predict not-yet-manifested
problems. Consequently, our benchmarks are performance problems that have already
happened in real world, and we will reproduce these problems to evaluate \Tool.
To conduct a thorough evaluation, we use
benchmarks from two sources.

First, we evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla that can no longer be
compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
When we extract code, we try our best to keep all bug-related data structures,
caller functions, and callee functions intact, and re-implement them in C++, 
following the original data flow and control flow. For these extracted benchmarks, 
we design bug-triggering inputs for them based on the bug-triggering inputs in 
the original bug reports and our understanding about how original program inputs
map to the inputs of our re-implemented programs.
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}. 
We will refer to this set of bugs as our \emph{general} benchmark suite.

Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
listed in Table \ref{tab:root}, but they are too difficult to be reproduced
on our machines.
First, they all depend on 
special hardware/software environment that our machine is not equipped with.
For example, some bugs can only be triggered on Windows, and some bugs depend on 
.Net libraries. 
Furthermore, the bug-related code for these 27 cases
cannot be easily extracted or reimplemented, as we did for the eight 
benchmarks mentioned above. 
For example, some bugs are related to GUI widgets, which are too complicated to 
re-implement or emulate. As another example, some bugs' inefficient 
loops traverse big graphs. Although we can extract the buggy code regions, it is 
too difficult to figure out the bug-triggering inputs
(i.e., the graphs) without reproducing the original bugs.

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of these 21 bugs.
Due to the focus of Toddler, all of these bugs 
are related to misusing basic data structures in Java, like ArrayList, HashSet, 
HashMap, and LinkedList. We extract these bugs and re-implemented them in 
C/C++, following the procedure discussed above. In doing so,
we also re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. At the end, each extracted benchmark contains at least five
loops, except for two cases where only 4 loops exist in the extracted version. 
Note that, Toddler focuses on inefficient nested loops, and hence its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.

We use Toddler benchmark suite for two reasons.
First, it was set up for completely different reasons and methodology from our
\emph{general} benchmark suite,
and hence can well complement the latter suite.
Second, it provides the largest set of 
repeatable inefficient loop problems that we can find.

@@

For all benchmarks we use, real-world
users have provided at least one problem-triggering input in their on-line 
bug bugs. We use these inputs in our run-time analysis.

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:benchmarks}. 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 33 out of \allbugs cases.

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287 and Apache\#53622, the root-cause loops contain both
cross-loop redundancy and 0*1? inefficiency. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
acknowledge both types of inefficiencies, but the patches
only changed the data structures, which eliminated both types of inefficiencies 
in case of MySQL\#27287 and left the cross-loop redundancy unsolved in
Apache\#53622. 
%For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? inefficient. 
%\Tool suggests batching and changing data structure, respectively. 
%In practice, developers only fix the main root cause loop, by using changing data structure.}

Second, the fix strategy taken by developers is related but not exactly the same as
what suggested by \Tool.
The root-cause loops in 
Collections bugs \#407, \#408, and \#425 all conduct frequent linear searches in arrays.
\Tool suggests data-structure changes for these three cases. Developers' patches 
still keep the original data structure and the original buggy loop, but they
did use hash-sets, which contain the same content as the arrays do,
to help conditionally skip the loops.

@@

As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
false positive and 22 benign false positives for all the top 5 loops
of the \allbugs benchmarks.

Here, benign false positives mean that the \Tool analysis result is true ---
some loops are indeed cross-iteration/loop redundant or indeed producing
results in only a small portion of all the iterations. However, those
problems are \textit{not} fixed by developers in their performance patches.

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 20 out of the
22 benign cases. % 11 out of 13 in the first benchmark set 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
%{\color{red} For example, there are 26 
For example, our run-time analysis has correctly pruned out 24 false positives
in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
top-5 suspicious loops in one of our benchmarks; it only generates side effect
in its last iteration, and hence is identified as by \Tool static analysis. 
Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies them as false positives. Similarly, \Tool run-time analysis
helps prune out 19 false positives for [0$|$1]* loop identification.

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC\#12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 has the largest overhead (4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC\#12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking. 
%XXX

@@

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed in Section \ref{sec:intro}, although these tools are very
useful, they are not suitable for failure diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs. 
We expect it to automatically detect a sub-set of the cross-loop redundancy
loops in our benchmark set, but not for other types of inefficient
loops. In summary, \Tool aims to explain performance problems that have 
already manifested,
yet bug detection tools aim to predict problems that may not have manifested.
\Tool achieves higher generality and accuracy at the cost of the prediction
capability.

>>>>

\paragraph{Benchmarks}
Note that \Tool is a tool that helps diagnose already-manifested performance problems,
not a detection tool that can help predict not-yet-manifested
problems. Consequently, our benchmarks are performance problems that have already
happened in real world, and we will reproduce these problems to evaluate \Tool.
To conduct a thorough evaluation, we use
benchmarks from two different sources.

First, we evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla that can no longer be
compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
When we extract code, we try our best to keep all bug-related data structures,
caller functions, and callee functions intact, and re-implement them in C++, 
following the original data flow and control flow. For these extracted benchmarks, 
we design bug-triggering inputs for them based on the bug-triggering inputs in 
the original bug reports and the mapping relationship between inputs of original programs 
and re-implemented programs.
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}. 
We will refer to this set of bugs as our \emph{general} benchmark suite.

Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
listed in Table \ref{tab:root}, but they are too difficult to be reproduced.
First, they all depend on 
special hardware/software environment that our machines are not equipped with.
For example, some bugs can only be triggered on Windows, and some depend on 
.Net libraries. 
Furthermore, the bug-related code for these 27 cases
cannot be easily extracted or reimplemented, as we did for the eight 
benchmarks mentioned above. 
For example, some bugs are related to GUI widgets, which are too complicated to 
re-implement or emulate. As another example, some bugs' inefficient 
loops traverse big graphs. Although we can extract the buggy code regions, it is 
too difficult to figure out the bug-triggering inputs
(i.e., the graphs) without reproducing the original bugs.

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of these 21 bugs.
Due to the focus of Toddler, all of these bugs 
are related to misusing basic data structures in Java, like ArrayList, HashSet, 
HashMap, and LinkedList. We extract these bugs and re-implemented them in 
C/C++, following the procedure discussed above. In doing so,
we also re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. At the end, each extracted benchmark contains at least five
loops, except for two cases where only four loops exist in the extracted version.

We use Toddler benchmark suite for two reasons.
First, it provides a large set of 
repeatable inefficient loop problems that we can access. 
Second, it was set up for a completely different reason and with a different 
methodology from our
\emph{general} benchmark suite,
and hence can well complement the \emph{general} suite.
We should also note that, Toddler focuses on inefficient nested loops, and hence its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.

@@

For all benchmarks we use, real-world
users have provided at least one problem-triggering input in their on-line 
bug reports. We use these inputs in our run-time analysis.

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns). 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 33 out of \allbugs cases.

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287 and Apache\#53622, the root-cause loops contain both
cross-loop redundancy and 0*1? inefficiency. Consequently, \Tool suggests two
corresponding fix strategies. In practice, the developers
acknowledge both types of inefficiencies, but the patches
only changed the data structures, which eliminated both types of inefficiencies 
in case of MySQL\#27287 and left the cross-loop redundancy unsolved in
Apache\#53622. 
%For Apache\#53622, there are two buggy loops, one is cross-loop redundant, and the other is 0*1? inefficient. 
%\Tool suggests batching and changing data structure, respectively. 
%In practice, developers only fix the main root cause loop, by using changing data structure.}

Second, the fix strategy taken by developers is related to but not exactly the same as
what suggested by \Tool.
The root-cause loops in 
Collections bugs \#407, \#408, and \#425 all conduct frequent linear searches in arrays.
\Tool suggests data-structure changes for these three cases. Developers' patches 
still keep the original data structures and the original buggy loops, but they
did use hash-sets, which contain the same content as the arrays do,
to help conditionally skip the loops.

@@

As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
false positive and 22 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

Here, benign false positives mean that \Tool analysis result is true ---
some loops are indeed cross-iteration/loop redundant or indeed producing
results in only a tiny portion of all the iterations. However, those
problems are \textit{not} fixed by developers in their performance patches.

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 20 out of the
22 benign cases. % 11 out of 13 in the first benchmark set 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging or profiling can often
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
%{\color{red} For example, there are 26 
For example, our run-time analysis has correctly pruned out 24 false positives
in 0*1? inefficiency detection for our benchmarks. Each of these 24 loops is a
top-5 suspicious loops in one of our benchmarks; it only generates side effects
in its last iteration, and hence is identified as 0*1? by static analysis. 
Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the number of iterations of each loop instance and
correctly identifies them as false positives. Similarly, \Tool run-time analysis
helps prune out 19 false positives for [0$|$1]* loop identification.

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 still incurs the largest overhead (merely 0.49\%). 
The diagnosis results remain the same for all but
GCC\#12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 has the largest overhead (merely 4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC\#12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking. 
%XXX

@@

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed in Section \ref{sec:intro}, although these tools are very
useful, they are not designed for failure diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs, 
which arise if a program fragment repeatedly iterates over a data structure, such as an array or list, that has not been modified between successive traversals of the data structure.
Like Toddler, it targets nested loops.
We expect it to detect a sub-set of the cross-loop redundancy
loops and a sub-set of 0*1? resultless loops in our benchmark set.
In summary, \Tool aims to explain performance problems that have 
already manifested,
yet bug detection tools aim to predict problems that may not have manifested.
They are suitable for different usage scenarios.

### 2016-03-23 section/evaltax.tex
submitted version

\section{Evaluation of Taxonomy}
\label{sec:eval_taxonomy}

@@

\subsection{Caveats} 
We do not intend to overly generalize the evaluation results above.
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are still uncovered cases, like distributed systems, 
and scientific computation.

>>>>

\section{Assessment of Root-Cause Taxonomy}
\label{sec:eval_taxonomy}

@@

\subsection{Caveats} 
What presented above reflects our best effort in assessing our root-cause
taxonomy using a non-biased set of real-world inefficient loop problems that
have been perceived by users and fixed by developers.

The numbers presented above should be interpreted together with our methodology
and should not be overly generalized.
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are definitely uncovered cases, like problems in distributed systems
and scientific computing systems, and others.
